\thispagestyle{plain}

\section*{Acknowledgments}

\indent First and foremost, I want to highlight the education from my parents, Adelar and Valdete. Their lessons and guidance enabled me to stand where I am today, and I cannot put in words how grateful I am for their support.

Secondly, I want to say "I love you" to the girl that I met way back when I still was in high school. She has been supporting me ever since. It has been 8 years of love, partnership and friendship. Thank you very much my Dear Caroline!

Thirdly, I want to give a shout out for all the folks that experienced UFSC life with me and still in contact: Lari, Zimpel, Griep, Ion, Karina, Roberto, Ruan, Claudio, Gui, Alevato, Elder, Eiterer. Also other folks that come and go: Giu, Penteado, Pedro Lemos, Kupas, Tortato. Deni you are going to deliver my certificate at my graduation!! (If you are reading this, and your name did not make it to this list, you should get in touch with me!!). Moreover, I want to thank the people from the institution: the faculty of EEL and other departments, the public employees of UFSC, and the labs that gave an opportunity to me: the Spacelab and the LCS.

Finally, I want to thank to Neoway for the opportunity to develop this work. Specially the people from the Analytics Team! These people are the reason, for me, of Neoway being a great place to work. Thank you very much for Andre, Penha, Igor, Breno, Mariana, Leandro, Vitor, Roger, Yuri, Leonardo, Felix, and Manoel. Also, a shout out for other teams (like the girls from GG and guys of SEC), and other employees that are not in the company anymore, but somehow had their contributions to my career!
% Hope didn't miss someone



\cleardoublepageempty
